Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-04-28 lqg-strings.tex
Started section on Einstein-Cartan string

The action\eqref{eqn:modified-NG-action} is still manifestly Poincaré invariant, since it only contains derivatives of $X^{\mu}$, thus it's variations vanish under global translations as in
\begin{equation} \label{eqn:global-inf-transl-NG}
	X^{\mu} \mapsto X^{\mu} + \epsilon ^{\mu} ,
\end{equation}
thus $\delta (\partial _{a} X^{\mu}) = \partial _{a} (\delta X^{\mu}) = \partial _{a} \epsilon ^{\mu} \equiv 0$. As for Lorentz transformations, we have that
\begin{equation} \label{eqn:global-inf-LT-NG}
	X^{\mu} \mapsto X^{\mu} + \epsilon ^{\mu \nu} X_{\nu} ,
\end{equation}
and since every term in the action is of the form
\begin{equation} \label{eqn:NG-general-term-form}
	\partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} ,
\end{equation}
with $\epsilon ^{\mu \nu} = - \epsilon ^{\nu \mu}$, we see immediately that the transformation leaves the action unchanged:
\begin{equation*}
	\delta (\partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu}) =
\end{equation*}
\begin{equation*}
	= (\partial _{a} (\delta X^{\mu}) \partial _{b} X^{\nu} + \partial _{a} X^{\mu} \partial _{b} (\delta X^{\nu})) \eta _{\mu \nu} =
\end{equation*}
\begin{equation*}
	= (\epsilon ^{\mu \rho} \partial _{a} X_{\rho} \partial _{b} X^{\nu} + \partial _{a} X^{\mu} \partial _{b} X_{\rho} \epsilon ^{\nu \rho}) \eta _{\mu \nu} =
\end{equation*}
\begin{equation*}
	= \epsilon _{\nu \mu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} + \epsilon _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} =
\end{equation*}
\begin{equation} \label{eqn:vanishing-inf-LT-NG}
	= (\epsilon _{\mu \nu} + \epsilon _{\nu \mu}) \partial _{a} X^{\mu} \partial _{b} X^{\nu} \equiv 0
\end{equation}
by the anti-symmetry of $\epsilon _{\mu \nu}$. At face value, this action does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term. This stems from the fact that we are assuming the existence of a minimum quantum of area, so it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.

In the expression\eqref{eqn:modified-NG-action} we can see a duality between the first and second terms. If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
\begin{align} \label{eqn:modified-NG-action-v3}
	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \frac{2}{g \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
	                 & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \onehalf {g' \Delta'}\sqrt{- (h')^{-1}} \right),
\end{align}
which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as make the replacements $T \rightarrow T' = \frac{1}{2} {g \Delta} T $ and $ \frac{1}{2} {g \Delta} \rarrow \frac{1}{2} {g' \Delta'} = \frac{2} {g \Delta}$
This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($g \gg 1$) and weak coupling ($g \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.

@@

In the following we parameterise the string with $\tau = t$ and $\frac{\partial X}{\partial \sigma} \cdot \frac{\partial X}{\partial t}$. The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen such that the $\sigma$ parameter is parallel to the parameter $s$, which is the length along the string parameter and this implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation. From this, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
\begin{equation} \label{eqn:string-energy}
	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
\end{equation}
and the form of the wave equation maintains its shape as in
\begin{equation} \label{eqn:corrected-NG-wave-equation}
	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
\end{equation}
where the effective mass density and effective tension are given by
\begin{align}
	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
\end{align}

Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
\begin{equation} \label{eqn:sigma-parameterization}
	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} = \frac{E (q)}{T (F^+)^2} ,
\end{equation}
we find the wave equation
\begin{equation} \label{eqn:simplified-modified-wave-eqn}
	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
\end{equation}
from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
\begin{equation} \label{eqn:wave-speed-corrected}
	v = \frac{c}{F^+}.
\end{equation}
This is in fact an expected result for a effective theory emerging from a discretised background geometry, see\cite{Bodendorfer-LQG}.

@@

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string. We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} .
\end{multline}
The reason for considering this form and not one in which the inverse metric $g^{a b}$ also gets a correction term is that this form of a Polyakov inverse area-corrected action reduces nicely to the Nambu-Goto corrected action(\ref{eqn:modified-NG-action}) when the auxiliary metric $g_{a b}$ coincides with the induced metric $h_{a b} = \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu}$. This action has the same properties as\eqref{eqn:modified-NG-action}: it is not reparameterisation invariant but is evidently Poincaré-invariant by the same arguments as before.

The equations of motion for the auxiliary metric are completely unchanged by this correction, so they are
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
\end{equation}
from which we obtain the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} \eta _{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} \eta _{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} .
\end{equation}

As for variation w.r.t the embbeding fields $X^{\lambda}$, we have
\begin{equation} \label{eqn:vary-wrt-X}
	\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
\end{equation}

\begin{multline} \label{eqn:X-eom-inverse-area}
	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} \eta _{\lambda \nu} + \\
	+ \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} \eta _{\lambda \nu} = 0 ,
\end{multline}
where $F^{-} = 1 - k \Delta / 2 (- g)$. In conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
\begin{equation} \label{eqn:X-eom-simplified}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \partial _{a} \ln (F^{-}) \partial _{b} X^{\mu} = 0 .
\end{equation}

@@

Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\phi (x)$ appearing in $F^{-}$. By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
\begin{equation}
	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0 ,
\end{equation}
from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation} \label{eqn:derivatives-F-minus}
	\partial _{\tau} \ln (F^{-}) = i E , \ \partial _{\sigma} \ln (F^{-}) = i p ,
\end{equation}
thus we have
\begin{equation} \label{eqn:ln-F}
	\ln (F^{-}) = i (E \tau + p \sigma) + a , \ a \in \mathbb{C}
\end{equation}

\begin{equation} \label{eqn:F-minus-exp}
	F^{-} = A \e ^{i (E \tau + p \sigma + \varphi)} , \ A > 0
\end{equation}
\begin{equation} \label{eqn:phi}
	\phi (\tau , \sigma) = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma + \varphi)} \right)}} .
\end{equation}
At first glance it seems problematic that we have a complex conformal factor $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it will also pick the respective component of $\phi$. With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
\begin{equation} \label{eqn:X-Klein-Gordon-eqn}
	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}
The modification to the dispersion relation via the mass term is also an expected effect of a discrete background geometry as mentioned in\cite{Bodendorfer-LQG}.

@@

At first glance, our recent analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string. However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found). While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence.

@@

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they're precisely the same as the ones of regular String Theory. What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
\end{multline}
with $E_{p} = \sqrt{p^2 + \mu ^2}$ for the closed string. From here on, we shall deal only with closed strings, unless otherwise stated. Following an analogous procedure to the one found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation} \label{eqn:reality-consequence}
	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
\end{equation}

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p}              & := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu} = 0 , \ \forall \ n , p \in \mathbb{Z} \label{eqn:"Virasoro"-modes-1} \\
	\widetilde{L} _{n , p} & := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{- p})^{*} \eta _{\mu \nu} = 0 , \ n \neq - p \label{eqn:"Virasoro"-modes-2}
\end{align}
\begin{equation} \label{eqn:"Virasoro"-modes-sum}
	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
\end{equation}

Before proceeding, we have one more remark: the 0-th term of the solution reads
\begin{equation} \label{eqn:X-sol-0-term}
	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
\end{equation}
which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) \sim \mu$. Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
\begin{equation} \label{eqn:a-p-relation}
	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation}

After analysing closer the $n = - p$ constraint(\ref{eqn:"Virasoro"-modes-sum}), we get the string mass in terms of vibrational modes and center of mass position
\begin{multline} \label{eqn:string-rest-mass}
	M^2 = - p^{\mu} p_{\mu} = \frac{1}{(4 \pi (\alpha ')^2)^2} \Bigg( (2 \pi \alpha ' m)^{2} x^{\mu} x_{\mu} - \\
	- \sum _{n \neq 0} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) a^{\mu} _{n} (a^{\nu} _{n})^{*} \eta _{\mu \nu} \right) \Bigg) .
\end{multline}

Collecting our results, we have that the solution for our closed string is given by
\begin{multline} \label{eqn:KG-Polyakov-solution-final}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
\end{multline}
subject to the family of constraints
\begin{equation} \label{eqn:"Virasoro"-constraints}
	L_{n , p} = \widetilde{L}_{n , p} = 0
\end{equation}
\begin{equation*}
	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
\end{equation*}
and 0-th oscillator mode related to center of mass position and momentum
\begin{equation*}
	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation*}
One thing to note is that the constraint(\ref{eqn:"Virasoro"-modes-2}) implies we only have $D$ non-zero modes in the solution, since all modes must be mutually orthogonal.

\subsection{The Modes and Constraints Algebra} \label{sec:modes-constraint-algebra}

>>>>

The action \eqref{eqn:modified-NG-action} has some interesting properties. First, on the face of it it does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term. Given that we are assuming the existence of a minimum quantum of area, it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory. However, if we look at that expression we see that it can be written as:
\begin{equation} \label{eqn:modified-NG-action-v2}
	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {g \Delta}{\sqrt{- (h^{-1})}} \right),
\end{equation}
where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$. So, while the second term is not diffeomorphism invariant \wrt the original metric $h_{ab}$ it is clearly diffeomorphism invariant \wrt the inverse metric $h^{ab}$.

Second, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms. If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
\begin{align} \label{eqn:modified-NG-action-v3}
	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \frac{2}{g \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
	                 & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \onehalf {g' \Delta'}\sqrt{- (h')^{-1}} \right),
\end{align}
which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as make the replacements $T \rightarrow T' = \frac{1}{2} {g \Delta} T $ and $ \frac{1}{2} {g \Delta} \rarrow \frac{1}{2} {g' \Delta'} = \frac{2} {g \Delta}$
This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($g \gg 1$) and weak coupling ($g \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.

@@

Using the static gauge $\tau = t$ and the transverse gauge with $\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0$, where $s$ is the length along the string parameter, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
\begin{equation} \label{eqn:string-energy}
	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
\end{equation}
and the form of the wave equation maintains its shape as in
\begin{equation} \label{eqn:corrected-NG-wave-equation}
	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
\end{equation}
where the effective mass density and effective tension are given by
\begin{align}
	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
\end{align}

Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
\begin{equation} \label{eqn:sigma-parameterization}
	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} = \frac{E (q)}{T (F^+)^2} ,
\end{equation}
we find the wave equation
\begin{equation} \label{eqn:simplified-modified-wave-eqn}
	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
\end{equation}
from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
\begin{equation} \label{eqn:wave-speed-corrected}
	v = \frac{c}{F^+}.
\end{equation}

@@

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string. we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}
The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
from which we obtain the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{equation}

As for variation w.r.t the embbeding fields $X^{\lambda}$, we have
\begin{equation} \label{eqn:vary-wrt-X}
	\frac{\delta S_{I A P}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}

\begin{multline} \label{eqn:X-eom-inverse-area}
	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
\end{multline}
where $F^{-} = 1 - k \Delta / 2 (- g)$. Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
\begin{equation} \label{eqn:X-eom-simplified}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \partial _{a} \ln (F^{-}) \partial _{b} X^{\mu} = 0 .
\end{equation}

@@

Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal function $\phi (x)$ appearing in $F^{-}$. By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
\begin{equation}
	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0 ,
\end{equation}
from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation} \label{eqn:derivatives-F-minus}
	\partial _{\tau} \ln (F^{-}) = i E , \ \partial _{\sigma} \ln (F^{-}) = i p ,
\end{equation}
thus we have
\begin{equation} \label{eqn:ln-F}
	\ln (F^{-}) = i (E \tau + p \sigma) + a , \ a \in \mathbb{C}
\end{equation}

\begin{equation} \label{eqn:F-minus-exp}
	F^{-} = A \e ^{i (E \tau + p \sigma + \varphi)} , \ A > 0
\end{equation}
\begin{equation} \label{eqn:phi}
	\phi (\tau , \sigma) = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma + \varphi)} \right)}} .
\end{equation}
At first glance it seems problematic that we have a complex conformal function $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\phi$. With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
\begin{equation} \label{eqn:X-Klein-Gordon-eqn}
	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}

@@

At first glance, our recent analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string. However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found). While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence, but ironically enough the calculations lead to the conclusion that the wave speed $v = 1 / F^{+}$ is actually time independent.

@@

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they're precisely the same as the ones of regular String Theory. What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
\end{multline}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. From here on, following an analogous procedure to the one found in \cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation} \label{eqn:reality-consequence}
	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
\end{equation}

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p}              & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-1}         \\
	\widetilde{L} _{n , p} & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-2} .
\end{align}

Before proceeding to quantization, we have one last remark: the 0-th term of the solution reads
\begin{equation} \label{eqn:X-sol-0-term}
	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
\end{equation}
which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) = 0$. Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
\begin{equation} \label{eqn:a-p-relation}
	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation}
Since our Virasoro-like \textquotedblleft modes" are double-indexed without summation, the string rest mass $M^2$ is given only in terms of the 0-th oscillator mode
\begin{equation} \label{eqn:string-rest-mass}
	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} \alpha ^{\mu} _{0} \alpha ^{\nu} _{0} \eta _{\mu \nu} .
\end{equation}

Collecting our results, we have that the solution for our string is given by
\begin{multline} \label{eqn:KG-Polyakov-solution-final}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
\end{multline}
subject to the infinite family of constraints
\begin{equation}
	L_{n , p} = \widetilde{L}_{n , p} = 0
\end{equation} \label{eqn:"Virasoro"-constraints}
and 0-th oscillation mode related to center of mass momentum
\begin{equation*}
	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation*}
